---
title: "Assignment 12"
author: "Sriya Reddy"
date: "2023-04-02"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

For this assignment, I used my code from a previous assignment and ported it to a Word file. I followed the code I wrote for Assignment 7 where I used different functions on the mtcars dataset.

I loaded the data into the variable `cars` with the command


```{r}
cars <- mtcars
cars
```


I used the head command to get 6 rows of the dataset

```{r}
head(cars)
```
The function plot generates the follwoing plot. 
```{r}
plot(cars)
```

The summary function provides the mean, median, quartiles and min/max values for each parameter. 
```{r}
summary(cars)
```

Earlier, I had created a function to generate the histogram for the histogram of the carb. I obtain the following plot. 
```{r}
car_func <- function(x, ...)
  UseMethod("car_func")
car_func.carb_hist <- function(x) hist(x$carb)
car_func.carb_hist(cars)
```
This is the markdown file for my code. 
The process of creating the Word/PDF/HTML file from the code directly is super interesting and easy to use!
